An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
updated gitignore to avoid some conflicts; cleaned up some within docs refs
Signed-off-by: andrew <andrew@textile.io>

In Textile, the interface to Logs is managed as a Thread. As mentioned previously, a Thread is a collection of Logs on a given topic. Threads are an event-sourced, distributed database, and can be used to maintain a single, collaboratively edited, watched, or hosted dataset across multiple Peers. Threads provide the mechanism to combine multiple Logs from individual authors into singular shared states through the use of either cross-Log sequencing (e.g. using a Bloom Clock, Merkle-Clock, or Hybrid Logical Clock [ref]) or a CRDT (see section xx).

@@

\begin{definition}
(Random Number). A random number of a user-specified length. 16 bytes or more.
\end{definition}

@@

\begin{definition}
(Raw). This variant declares that consumers are not expected to make additional assumptions. This is the default variant. 
\end{definition}

Example (V1, 128 bit): `bafkxd5bjgi6k4zivuoyxo4ua4mzyy`

\begin{definition}
(Access-Controlled): This variant declares that consumers should assume an access control list is composable from Log Events. The ACL represents a permissions rule set that must be applied when reading data (see Section  \ref{sec:AccessControl}).
\end{definition}

\begin{example}
\begin{lstlisting}
"bafyoiobghzefwlidfrwkqmzz2ka66zgmdmgeobw2mimktr5jivsavya"
\end{lstlisting}
\caption{V1, 256 bit.}
\end{example} \label{ex:v1256}

@@

\begin{definition}
(Sequence). An Event Sequence is a series of ordered events referring to a specific entity or object. For example, an ACL JSON document is a single entity made up of a sequence of Thread Events. A Sequence might have a unique UUID (.e.g, id =bafykrq5i25vd64ghamtgus6lue74k) as in the example below.
\end{definition}

fixidexampleabove

>>>>

In Textile, the interface to Logs is managed as a Thread. As mentioned previously, a Thread is a collection of Logs on a given topic. Threads are an event-sourced, distributed database, and can be used to maintain a single, collaboratively edited, watched, or hosted dataset across multiple Peers. Threads provide the mechanism to combine multiple Logs from individual authors into singular shared states through the use of either cross-Log sequencing (e.g. using a Bloom Clock, Merkle-Clock, or Hybrid Logical Clock [ref]) or a CRDT.

@@

\begin{definition}
(Random Number). A random number of a user-specified length. 16 bytes or more  (see Example \ref{ex:Identity}).
\end{definition}

@@

\begin{definition}
(Raw). This variant declares that consumers are not expected to make additional assumptions. This is the default variant.\\

See Example \ref{ex:Identity}).
\end{definition}

\begin{definition}
(Access-Controlled): This variant declares that consumers should assume an access control list is composable from Log Events. The ACL represents a permissions rule set that must be applied when reading data (see Section  \ref{sec:AccessControl}).\\

See Example \ref{ex:Identity}).
\end{definition}

\begin{example*}
\centering
\begin{minipage}{0.6\textwidth}
\begin{lstlisting}[language=json,firstnumber=1]
# Raw identity. V1, 128 bit
bafkxd5bjgi6k4zivuoyxo4ua4mzyy

# ACL enabled identity. V1, 256 bit.
bafyoiobghzefwlidfrwkqmzz2ka66zgmdmgeobw2mimktr5jivsavya
\end{lstlisting}
\end{minipage}
  \caption{Identity variants.}
  \label{ex:Identity}
\end{example*}

@@

\begin{definition}
(Sequence). An Event Sequence is a series of ordered events referring to a specific entity or object. For example, an ACL JSON document is a single entity made up of a sequence of Thread Events. A Sequence might have a unique UUID (see Example \ref{ex:SequenceID}) as in the example below.
\end{definition}

\begin{example}
\centering
\begin{lstlisting}[language=json,firstnumber=1]
# UUID
bafykrq5i25vd64ghamtgus6lue74k
\end{lstlisting}
  \caption{Sequence ID.}
  \label{ex:SequenceID}
\end{example}
